Supplementary Content

### 2022-02-07 experiments/2_supplement/supplement.Rmd
Update supplement.Rmd

---
title: Supplementary Content
subtitle: Functional diversity ... Predictions of a model of an oxic-anoxic microbial ecosystem 
author: "Owen L Petchey, Rainer Krug, Marcel Suleiman, ???others???"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
---

>>>>

---
title: Supplementary Content
subtitle: Functional diversity ... Predictions of a model of an oxic-anoxic microbial ecosystem 
author: "Owen L Petchey, Rainer Krug, Marcel Suleiman, Romana Limberger, ???others???"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
---
